TAPIR: Threaded Application Programming on Intermittent Resources

### 2017-05-11 paper.tex
Fixed missing citations

\section{Related Work} -Emily
In addition to the division of a program into tasks, as described above, prior work
explores several different strategies for preserving state across reboots. The approaches
range from fully independent of the programmer~\cite{ratchet, dewdrop} at one extreme, to programmer
defined task boundaries~\cite{dino} at the other.  Compiler driven approaches such as the
method used in ~\cite{Mementos} allow the programmer to specify high level behavior of the
checkpointing system. A key similarity among the prior work is it
does not lend itself well to multi-programming let
alone multi-threading. In fact, many of these works state the assumption that the device
hardware cannot support a conventional OS, and thus focus on single threaded programs. 
Despite the availability of (relatively) inexpensive nonvolatile memory technology such as
FRAM~\cite{quickrecall}, the the energy and storage overhead of checkpointing multiple
thread states would limit the maximum per-thread checkpoint size.

>>>>

\section{Related Work} 
In addition to the division of a program into tasks, as described above, prior work
explores several different strategies for preserving state across reboots. The approaches
range from fully independent of the programmer~\cite{ratchet, dewdrop} at one extreme, to programmer
defined task boundaries~\cite{Dino} at the other.  Compiler driven approaches such as the
method used in ~\cite{Mementos} allow the programmer to specify high level behavior of the
checkpointing system. A key similarity among the prior work is it
does not lend itself well to multi-programming let
alone multi-threading. In fact, many of these works state the assumption that the device
hardware cannot support a conventional OS, and thus focus on single threaded programs. 
Despite the availability of (relatively) inexpensive nonvolatile memory technology such as
FRAM~\cite{quickrecall}, the the energy and storage overhead of checkpointing multiple
thread states would limit the maximum per-thread checkpoint size.
